RD design analysis

### 2024-07-05 analysis/RD design analysis.Rmd
modified:   analysis/RD design analysis.Rmd 	deleted:    analysis/RD-design-analysis.log 	deleted:    analysis/placebo-test/coefficients.dta 	deleted:    analysis/placebo-test/~permute_neighbor.do.stswp 	new file:   plotting/placebo_plot.R

```{r}
# these are the packages that we need to import
library(dplyr)
library(haven)
library(rdd)
library(ggplot2)
library(dplyr)
library(rdrobust)
library(plm)
library(xtable)
library(pander) # this is for table showing
library(latex2exp) # this is to export it
setwd("E:/umich/RealEstateBrokerage-main")
# need to place data on the base directory
data <- read_dta("template.dta")
working_directory <-"E:/umich/RealEstateBrokerage"
```

>>>>

```{r}
# these are the packages that we need to import
library(dplyr)
library(haven)
library(rdd)
library(ggplot2)
library(rdrobust)
library(plm)
library(xtable)
library(pander) # this is for table showing
library(latex2exp) # this is to export it
setwd("E:/umich/RealEstateBrokerage-main")
# need to place data on the base directory
data <- read_dta("template.dta")
working_directory <-"E:/umich/RealEstateBrokerage"
```
